Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2011-12-16 article/Article.tex
ajoute les equations de la partie maths

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$} {\small{and}} David Legland{$^2$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et Reproduction, Jouy en Josas, F-78350, France.\\
{$^2$}INRA, XXX, France.}

@@

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$} {\small{and}} David Legland{$^2$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du D\'eveloppement et Reproduction, Jouy en Josas, F-78350, France.\\
{$^2$}INRA, UMR 0782, G\'enie et Microbiologie des Proc\'ed\'es Alimentaire, Thiverval-Grignon, F-78850, France.}

@@

% Crofton formula
Perimeter measure of 2D objects, surface area measure of 3D objects 
and more generally $(d-1)$-surface measure of $d$-dimensional objects 
can be expressed in a unified formalism by using the Crofton formula.
This formula consists in integrating the intercept number of the object with
lines of various orientation and positions. Its expression in
the general form is:
\begin{eqnarray}
S^{(d-1)}(X) & = & \frac{d v_d}{\pi}\int_{\mathcal{L}^d}\chi\left(X\cap L\right) dL
\end{eqnarray}
where $X$ is the structure of interest, $v_d$ is the volume of the $d$-dimensional ball,
$\mathcal{L}^d$ is the set of all lines in the $d$-dimensional space. 
The Euler-Poincar\'e characteristic $\chi$ is equal to number of connected components
of the intersection of $X$ with a line $L$.

% 2D and 3D
For planar and 3D cases, Equation 1 can be rewritten:
\begin{eqnarray}
P(X) & = & \pi \int_{\mathcal{L}^2} \chi \left( X \cap L \right) dL \\
S(X) & = &  4  \int_{\mathcal{L}^3} \chi \left( X \cap L \right) dL
\end{eqnarray}

% discretisation
The Crofton formula can be easily applied to discrete binary images. 
The integral over lines can be decomposed into an integral over a finite set of directions
and an integral over lines parallel to a given direction.
